Measurement Bias from Address Aliasing

### 2014-05-02 paper.tex
=Minor change to abstract only.

    In this paper we show how an optimization in the out-of-order execution engine on modern Intel microarchtectures can affect performance depending on run-time memory layout.

>>>>

	% Bad motivation start:
    % In this paper we show how an optimization in the out-of-order execution engine on modern Intel microarchtectures can affect performance depending on run-time memory layout. 
    In this paper we identify the underlying mechanics resulting in measurement bias on modern Intel microarchtectures. 
    The magnitude of this performance bias has been shown to be significant, and can be as high as a factor two.
